---
title: "Visualization"
author: "Wentong"
date: "10/9/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
```

## Load the weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>% ## is going to go online and download the data
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Scatterplots!

Create my first scatterplot ever.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

New approach, same plot.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Save and edit a plot object.

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot +geom_point(
)
```

## Advance scatterplot...

Start with the same one and make it fancy!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

What about the `aes` placment...?
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) +
  geom_smooth()
```

Let's facet some things!!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax,  color = name)) + 
  geom_point(alpha = .5) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

Let's combine some elements and try a new plot!
```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) + ## prcp data was divided
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


## Some small notes

How many geoms have to exist?

You can have whatever geoms you want.
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom!
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() + 
  geom_point(alpha = .3)
```








